---
title: 'Week 4: Linear Regression'
output: 
  html_document:
    mathjax: default
---

```{r,echo=FALSE}
# Setup the environment
# setwd("C:/Users/Owner/Google Drive/School/R-Audit Analytics II")
# options(scipen=8)
library(lattice)
library(CreditAnalysis)
```

Linear regression is useful in identifying linear relationships between two variables. If the points appear to fall along the same line when the dataset is visualized, then a relationship is likely to exist.  You can be sure of the relationship by testing for correlation.

The fist step in testing for linear regression is to plot the data.  As shown in the figure below, the data appears to fall along the red line.   The relationship is not exactly correlated because there are errors or spaces between the points and the line. Having errors does not preclude correlation since it is very unlikely to have all of the points fall exactly on the line. There does not appear to be any significant outliers either.

## Data Visualization  
```{r}
# Read in the data
data(Sales)

# Plot the data with regression line
p<- xyplot(Sales~Marketing,
         data=sales,
         type=c("p","r"),
         main= "Regression Example Data",
         par.settings=simpleTheme(col="red", col.points="blue",pch=20)
         )
p
```


After visualizing the data, the next step in performing linear regression is to perform a  correlation test to determine the coefficients of the line and to determine the statistical validity of the model.  As shown in the output below, the coefficients are B0= 301810.67 and B1=168.56.  The equation from these coefficients is:

$$Sales= 301,810.67 + 168.56*Marketing$$

This sign of the second coefficient is positive which tells us that sales do increase 
with Marketing spend.  The scale of the coefficients tells us that Marketing has a high
ROI because sales tends to increase by $168 for each dollar spent.  Before accepting 
these conclusions, we have to check the p value and R-squared.  Both of these values 
indicate how well the model fits the data.  The p-value is quite small for B1 and less 
than 0.05 meaning the value is significant at the 95% confidence interval.  The R
-squared value is 0.9567 indicating the amount of Sales variance explained by Marketing.
The compliment, 1-R-squared, is 0.433 and quantifies the amount variance in Sales that 
cannot be explained by Marketing.


```{r}
g<- glm(Sales~Marketing, data=sales)
summary.lm(g)
```
