---
title: "Credit Approval Analysis"
author: "Ryan Kuhn"
date: "May 1, 2015"
output: beamer_presentation
transition: faster
---

##Background

**Objective:**  
To demonstrate the analytical techniques taught during the Special Topics in Audit Analytics course at Rutgers University

**Data:**  
- Dataset- Credit Screening on Credit Card Applications  
- Source- UCI Machine Learning Repository

**Assumptions:**  
Field names and values changed to meaningless values. 
Made assumtions about what attributes the data represents.


## Research Question - 1

**Q:**  Is there a relationship between Age, Income, Credit Score, and Debt levels and the credit approval status? 
Can this relationship be used to predict if a person is granted credit? 
If yes, does the relationship indicate reasonable risk management strategies?

## Research Question - 1

**Q:**  Is there a relationship between Age, Income, Credit Score, and Debt levels and the credit approval status? 
Can this relationship be used to predict if a person is granted credit? 
If yes, does the relationship indicate reasonable risk management strategies?

**A:** Relationships exists between Prior default, Years employed, Credit score, and Income level. 
These variables are reasonable management strategies. 

## Research Question - 2

**Q:** Ethnicity is a protected status and the decision to approve or deny an application cannot be based on the applicant's ethnicity. 
Is there a statistically significant difference in how credit is granted between ethnicities that could indicate bias or discrimination? 

>H0: Ethnicity and approval are independent.  
>H1: Approval status is associated with the ethnicity and credit card company has a compliance risk.

## Research Question - 2

**Q:** Ethnicity is a protected status and the decision to approve or deny an application cannot be based on the applicant's ethnicity. 
Is there a statistically significant difference in how credit is granted between ethnicities that could indicate bias or discrimination? 

>H0: Ethnicity and approval are independent.  
>H1: Approval status is dependent on the ethnicity and credit card company has a compliance risk.

**A:**  A chi-squared test did not give evidence that ethnicity and approval status are dependent. 
We cannot reject the null hypothesis.

##Analytic Methods Used

Methods used: 

- Linear regression 
- Descriptive Statistics and Normalization
- Association Rules 
- Logistic regression
- Classification and Regression Tree
- Ensembling

##Linear Regression

Used to fill in missing values in Age

```{r environment, echo=FALSE, results='hide', warning=FALSE,message=FALSE}
# Set the environment
suppressWarnings(require(knitr,   quiet=T))
suppressWarnings(require(ggplot2, quiet=T))
suppressWarnings(require(dplyr,   quiet=T))
suppressWarnings(require(reshape2,quiet=T))
suppressWarnings(require(ROCR,    quiet=T))
suppressWarnings(require(caTools, quiet=T))
suppressWarnings(require(rpart,   quiet=T))
suppressWarnings(require(rpart.plot, quiet=T))
suppressWarnings(require(arules,  quiet=T))
suppressWarnings(require(arulesViz,quiet=T))
suppressWarnings(require(scales,  quiet=T))
suppressWarnings(require(dplyr,  quiet=T))


options(scipen=6, width=100)
opts_knit$set(width=75)
setwd("C:/Users/Ryan/Google Drive/School/R-Audit Analytics II/Project")
opts_chunk$set(echo=F, 
               message=F, 
               warning=F, 
               comment=NA)
```

```{r loadData}
#Download the data
myURL<- "http://archive.ics.uci.edu/ml/machine-learning-databases/credit-screening/crx.data"
if(!file.exists("Dataset.csv")){
    download.file(myURL,"Dataset.csv")
    }
rm(myURL)

# Load the data
Cols<- c(rep("character",2),"numeric",rep("character",4),"numeric",rep("character",2),
         "numeric",rep("character",3),"numeric","character")
Data<-read.csv("Dataset.csv",sep=",",colClasses=Cols)
rm(Cols)

# Give column names by letter
# names(Data)<- LETTERS[1:16]
names(Data)<-c("Male","Age","Debt","Married","BankCustomer","EducationLevel","Ethnicity","YearsEmployed","PriorDefault","Employed","CreditScore","DriversLicense","Citizen","ZipCode","Income","Approved")
```

```{r str, echo=F, results='hold'}
# Convert binary values to 1 or 0
Data$Male<- ifelse(Data$Male=="a",1,0)
Data$Employed<- ifelse(Data$Employed=="t",1,0)
Data$PriorDefault<-ifelse(Data$PriorDefault=="t",1,0)
```

```{r transformations}
# Convert credit granted to 1 or 0
Data$Approved<-ifelse(Data$Approved=="+",1,0)
Data$Approved<-factor(Data$Approved)

Data[Data=="?"]<-NA
```

```{r}
Data$Age<-as.numeric(Data$Age)
Numeric<- Data[,c(2:3,8,11,15)]

Mean.Age<- mean(Numeric$Age,na.rm=T)

SD.Age<-round(sd(Numeric$Age, na.rm=T),4)
```

```{r correlations}
round(cor(Numeric,use="complete.obs"),3)

AgeMdl<-lm(Age~YearsEmployed, data=Data,na.action=na.exclude)
AgeMdl$coefficients
```


## Descriptive Stats and Normalization
Convert values to Z-Scores

```{r transformation, fig.height=3}
#Convert to z score
SD.Age<-round(sd(Numeric$Age, na.rm=T),4)
Data$AgeNorm<- (Data$Age-mean(Data$Age, na.rm=T))/SD.Age
rm(SD.Age, Mean.Age)

# View the distribution
par(mfrow=c(1,2), oma=c(0,0,.75,0))
hist(Data$Age,main=NULL,xlab="Age",col="blue")
hist(Data$AgeNorm,main=NULL,xlab="AgeNorm",ylab=NULL,col="green")
title("Distribution of Values Before and After Normalization",outer=T)
```

```{r plotage, fig.height=2}
ggplot(Data) + 
    aes(Approved,AgeNorm) + 
    geom_boxplot(outlier.colour="red") +
    theme_bw() +
    coord_flip() +
    labs(title="Distribution of AgeNorm by Credit Approval Status")
```

```{r}
# Scale the variables
Temp<- data.frame(scale(Data[,c(3,8,11,15)],center=T,scale=T))
colnames(Temp)<-c("DebtNorm","YearsEmployedNorm","CreditScoreNorm","IncomeNorm")
Data<-cbind(Data,Temp)
rm(Temp)
```

```{r}
Temp<- data.frame(scale(log(Data[,c(3,8,11,15)]+1),center=T))
names(Temp)<-c("DebtLog","YearsEmployedLog","CreditScoreLog","IncomeLog")
Data<-cbind(Data,Temp)
rm(Temp)
```

```{r, results='hide'}
dev.off()

# Simplify dataset to remove transformed points
Data<- Data[,-c(2,3,8,11,15,18:21)]
```

## Association Rules


```{r}
Data$Married<-ifelse(is.na(Data$Married),"u",Data$Married)
Data$BankCustomer<-ifelse(is.na(Data$BankCustomer),"g",Data$BankCustomer)
Data$Ethnicity<-ifelse(is.na(Data$Ethnicity),"v",Data$Ethnicity)
Data$EducationLevel<-ifelse(is.na(Data$EducationLevel),"c",Data$EducationLevel)
Data$ZipCode<-ifelse(is.na(Data$ZipCode),"00000",Data$ZipCode)
Data$Male<-ifelse(is.na(Data$Male),"b",Data$Male)
```

```{r}
# Convert categorical variables to factors
Data[,1:10]<- lapply(Data[1:10],function(x) factor(x))

Data$Ethnicity<-relevel(Data$Ethnicity,"v")
```

```{r apriori, results='hide'}
# Generate rules
Rules<- apriori(Data[!incomplete,1:10], 
                parameter=list(supp=0.1,
                               conf=0.75,
                               target='rules'))


```

```{r, fig.height=4}

subRules<-head(sort(Rules, by="lift"),15)
# plot(subRules,method="graph", control=list(type="items", alpha=0.8))


# Use for example
    # First, convert row to transaction set
basket<-as(Data[248,1:10],"transactions")

    # Find rules wher the rhs equals A.  These rules imply the value in column A.
Match.RHS<- subset(Rules, subset= rhs %pin% "Male")

    # Of subset of rules, find those where the lhs is a subset of the items in the target row
Match.LHS<-is.subset(Match.RHS@lhs, basket)
```
1. Support: Support is how often the left hand side of the rule occurs in the dataset. 
In our example above, we would count how many times {u,g,c} occurs and divide by the total number of transactions.

2. Confidence: Confidence measures how often a rule is true. 
First, we find the subset of all transactions that contain {u,g,c}. 
Of this subset, we then count the number of transactions that match the right hand side of rule, or {1}. 
The confidence ratio is calculated by taking the number of times the rule is true and dividing it by the number of times the left hand side occurs.  


```{r}
# View the rules
inspect(Match.RHS[Match.LHS])
```
## Baseline Model

- Simple mean of results. 
- Establish benchmark to measure model accuracy 
- 

```{r}
Train %>%
    summarise(Total=n(), Success=sum(Approved==1)) %>%
    mutate(Percent=round(Success/Total*100,2))
```

## Logistic Regression

```{r samplesplit}
set.seed(1234)

split<- sample.split(Data$Approved, SplitRatio=0.75)
Train<- subset(Data,split==TRUE)
Test <- subset(Data, split==FALSE)

rm(split)
```

```{r logmodel}
LogFit<- glm(Approved~AgeNorm+DebtLog+YearsEmployedLog+CreditScoreLog+IncomeLog, data=Train,family=binomial)
summary(LogFit)
```

```{r}
LogPred<- predict(LogFit,newdata=Train, type="response")
table(Train$Approved, LogPred>0.5)
```

## CART Model
```{r, fig.height=3}
set.seed(1234)
TreeFit<-rpart(Approved~Male+Married+BankCustomer+EducationLevel+Ethnicity+PriorDefault+Employed+DriversLicense+Citizen+AgeNorm+DebtLog+YearsEmployedLog+CreditScoreLog+IncomeLog, 
               data=Train, 
               method="class",
               control=rpart.control(xval=10,cp=0.025))

TreeFit

prp(TreeFit,main="CART model", digits=6, 
    extra=1,
    branch.col="blue",
    type=4,
    leaf.round=2,
    box.col=c("pink","palegreen")[TreeFit$frame$yval],
    ycompact=T)
```

## References

Data:  
http://archive.ics.uci.edu/ml/machine-learning-databases/credit-screening  

Analytic Report:  
http://www.rpubs.com/kuhnrl30/CreditScreen